---
title: "< STAT-5361 > HW#2-Exercises 3"
author: "Hee-Seung, Kim"
date: "September 13, 2018"
output: pdf_document
fontsize: 11pt
documentclass: article
knit: "bookdown::render_book('HW2-3_Hee.Rmd','bookdown::pdf_document2')"
papersize: letter
biblio-style: asa 
---
 
Explain how .Machine$double.xmax, .Machine$double.xmin, .Machine$double.eps, and .Machine$double.neg.eps are defined using the 64-bit double precision floating point arithmetic.


1) Description
(a) Machine() returns information on numeric characteristics of the machine R is running on, such as the largest double or integer and the machine's precision.
(b) .Machine is a variable holding this information.

2) .Machine$double.xmax <- the largest finite floating-point number. Typically, it is equal to (1 - neg.eps) * base^max.exp, but on some machines it is only the second, or perhaps third, largest number, being too small by 1 or 2 units in the last digit of the significand.
```{r}
.Machine$double.xmax
```
3) .Machine$double.xmin <- the smallest non-vanishing normalized floating-point power of the radix, i.e., base^min.exp.
```{r}
.Machine$double.xmin
```
4) .Machine$double.eps <- the smallest positive floating-point number x such that 1 + x != 1. It equals base^ulp.digits if either base is 2 or rounding is 0; otherwise, it is (base^ulp.digits) / 2
```{r}
.Machine$double.eps
```
5) .Machine$double.neg.eps <- a small positive floating-point number x such that 1 - x != 1. It equals base^neg.ulp.digits if base is 2 or round is 0; otherwise, it is (base^neg.ulp.digits) / 2. As neg.ulp.digits is bounded below by -(digits + 3), neg.eps may not be the smallest number that can alter 1 by subtraction.
```{r}
.Machine$double.neg.eps
```